Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-02 paper/paper.tex
latest

The models we use correspond to simplified geometrical configurations.
This allows us to perform a deep exploration of parameter space and
gain some physical insight into \tol's kinematic properties.
In this paper we show, for the first time in the literature, that \tol's
\lya profile can be explicitly modeled by either of these two
models. 
{\bf The hybrid case of a rotating multiphase configuration
is the subject of ongoing research (Remolina-Gutierrez et al. in
prep.)  as it cannot be simulated with existing models.  }

@@

\tol\ presents one of the most atypical \lya spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Recent Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial smapling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and promiment emission lines, this allowed them to produce 
two-dimensional velocitity field maps using the H$\alpha$ emission
line.
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }

@@

Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
{\bf This estimate should be considered an upper bound, lower values
  could be achieved if one considers instead a cored profile.}
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This estimate and the validity of its assumptions can only be
  verified by detailed mass modelling once \tol's full rotation curve
  becomes available.}

@@

In this particular case, we prefer the multiphase model because it has kinematic
conditions similar to those in similar compact dwarf galaxies observed
with integral field unit spectroscopy, while the
rotational model produces rotational velocities too high for a dwarf
galaxy.  
New IFU observations are the only way to be certain about the detailed
kinematic structure in \tol.

>>>>

The models we use correspond to simplified geometrical configurations.
This allows us to perform a deep exploration of parameter space and
gain some physical insight into \tol's kinematic properties.
In this paper we show, for the first time in the literature, that \tol's
\lya profile can be explicitly modeled by either of these two
models. 
{\bf The hybrid case of a rotating multiphase configuration
cannot be simulated with existing numerical implementations and 
is the subject of ongoing research (Remolina-Gutierrez et al. in
prep.) }

@@

\tol\ presents an atypical \lya spectrum. 
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

{\bf Which model could be closer to the actual kinematic conditions in \tol?  
Recent Integral Field Unit (IFU) observations of other CDGs seem to
favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial smapling was $0.67^{\prime\prime}$ and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and promiment emission lines to finally compute velocitity
field maps using the H$\alpha$ emission line. 
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120$ \kms) to highly irregular. 
The typical velocity dispersion values are in the range $10-50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms. }

@@

Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
{\bf This estimate should be considered an upper bound as lower values
  could be achieved if one considers instead a cored profile.}
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This estimate and the validity of its assumptions can only be
  verified by detailed mass modelling once \tol's full rotation curve
  becomes available.}

@@

In this particular case, we prefer the multiphase model because it has kinematic
conditions similar to other compact dwarf galaxies observed
with integral field unit spectroscopy, while the
rotational model produces rotational velocities too high for a dwarf
galaxy.  
New IFU observations are the only way to be certain about the detailed
kinematic structure in \tol.
